Portal Forecast

### 2017-09-28 index.Rmd

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance()
obs_data$total = rowSums(select(obs_data, -period))
new_moon_file = portalr::FullPath('PortalData/Rodents/moon_dates.csv', 
                                                  '~')
new_moons = read.csv(new_moon_file)
obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "period"))
obs_data_newmoon$censusdate = as.Date(obs_data_newmoon$censusdate)
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance("repo")
obs_data$total = rowSums(select(obs_data, -period))
new_moons = read.csv(text = RCurl::getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))

obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "period"))
obs_data_newmoon$censusdate = as.Date(obs_data_newmoon$censusdate)
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")
